---
title: "Municipals Vignette"
author: "Mohammed Bakheet, Chathuranga Silva and Nikodimos Gezahegn"
date: "05th October 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{municipals}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab05)
```

# Fitting Linear Models

``` municipals ``` is used to get Municipal data from the  'Kolada' API. It can be used to Search All Municipal in Sweden, Search Institutes in Sweden and Search Institutes within a specific Munipality. User can search data from the Shiny Application

# Usage
```c

 item <- municipals$new()
 item$createShiny()

```


# Value

An object of class ``` municipals ``` is a list containing at least the following components:

base_URL
  : Base URL for Kolada API.
  
all_data
  : All available Municipal Data(Including County Councils).
  
all_council_data
  : All available Country Council data.
  
all_municipal_data
  : All available Municipal data.
  
selected_municipal
  : Selected Municipal Name.
  
  
# Methods

getAllData()
  : Retrieve All Country and Municipal Data.
  
getOuData(municipalId, search_text)
  : Retrieve Institutes title includes search_text in given municipal.
  
getKpiData(search_text)
  : Retrieve All Institues data which title includes search_text.

getAllCouncilData()
  : Retrieve all Council data.
  
getAllMunicipalData()
  : Retrieve all Municipal data.

getMunicipalData(search_name)
  : Retrieve Municipal which title include data search_name.
  
createShiny()
  : Create Shiny app and show on browser.

# References

Kolada :- "https://www.kolada.se/index.php?_p=index#"
Rolada API Doc :- "https://github.com/Hypergene/kolada"

# Examples

```
item <- municipals$new()
item$getMunicipalData("Ale")
item$getKpiData()
item$createShiny()
```
